### 2015-03-07 paper_40_cri.tex
updated schedule in the case study
updated sensitivity analysis and conclusion added latest PDF file
rearranged some figures so they appear more inline with the appropriate content

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{6\sigma_i} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma^2$ is the estimated variance
                \end{itemize}

@@

                \[
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \]
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                \end{itemize}

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sub:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        flucate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then For more on sensitivity analysis 
                in statistical modeling, see \cite{Saltelli2000}.
        \end{description}

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring a software development organization. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\

>>>>

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects for Application ID $i$
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                \end{itemize}

@@

                \begin{equation}
                \label{eq:CDF}
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \end{equation}
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                \end{itemize}

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sec:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        flucate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then For more on sensitivity analysis 
                in statistical modeling, see \cite{Saltelli2000}.
        \end{description}

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring a software development organization. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\

### 2015-03-07 paper_50_sdlc-ae.tex
rearranged some figures so they appear more inline with the appropriate content

@@

    \begin{figure}[ht]
        \includegraphics[scale=.75]{images/sdlcae.png}
        \caption{SDLC ANALYTIC ENGINE}
        \label{fig:sdlc-ae}
    \end{figure}

@@

            The first set of tables that need to be created are tables
            to store the raw data that is collected.  These tables
            will line up with the necessary data for each of the 5 elements
            of CRI.  Figure \ref{fig:raw} provides a visual description
            of the tables that are needed.  The tables have no relationship
            with each other since they are raw data.  The primary goal of
            these tables is to store the raw data in a single database. The
            5 table names are:
            \begin{enumerate}
                \item QUALITY\_RAW
                \item AVAILABILITY\_RAW
                \item SATISFACTION\_RAW
                \item SCHEDULE\_RAW
                \item REQUIREMENTS\_RAW
            \end{enumerate}
            Notice these table names match with the 5 elements of CRI.

           \begin{figure}[ht]
                \centering
                \includegraphics[scale=.55]{images/raw_tables.png}
                \caption{TABLES FOR RAW CRI DATA}
                \label{fig:raw}
            \end{figure}

@@

           \begin{figure}[ht]
                \centering
                \includegraphics[scale=.55]{images/score_tables.png}
                \caption{TABLES FOR INTERMEDIATE CRI SCORES}
                \label{fig:score_tables}
            \end{figure}%

@@

           \begin{figure}[ht]
                \centering
                \includegraphics[scale=.55]{images/final_score_tables.png}
                \caption{TABLES FOR FINAL CRI SCORES}
                \label{fig:final_score_tables}
            \end{figure}

@@

%    \subsection{QUERIES}
%        The section will provide the necessary SQL queries to obtain the correct data
%        needed to compute the individual elements of CRI.
%        
%    \subsection{COMPUTATIONS}
%        This section will provide R scripts to calculate each individual score and the overall 
%        CRI score. The scripts will need to be run every time the data is updated and the CRI
%        score needs to be recalculated.

>>>>

    \begin{figure}[hbt]
        \includegraphics[scale=.75]{images/sdlcae.png}
        \caption{SDLC ANALYTIC ENGINE}
        \label{fig:sdlc-ae}
    \end{figure}

@@

@@

            The first set of tables that need to be created are tables
            to store the raw data that is collected.  These tables
            will match up with the necessary data for each of the 5 elements
            of CRI.  Figure \ref{fig:raw} provides a visual description
            of the tables that are needed.  The tables have no relationship
            with each other since they are raw data.  The primary goal of
            these tables is to store the raw data in a single location. The
            5 table names are:
            \begin{enumerate}
                \item QUALITY\_RAW
                \item AVAILABILITY\_RAW
                \item SATISFACTION\_RAW
                \item SCHEDULE\_RAW
                \item REQUIREMENTS\_RAW
            \end{enumerate}
            Notice these table names match with the 5 elements of CRI.

           \begin{figure}[htb]
                \centering
                \includegraphics[scale=.52]{images/raw_tables.png}
                \caption{TABLES FOR RAW CRI DATA}
                \label{fig:raw}
            \end{figure}

@@

           \begin{figure}[htb]
                \centering
                \includegraphics[scale=.52]{images/score_tables.png}
                \caption{TABLES FOR INTERMEDIATE CRI SCORES}
                \label{fig:score_tables}
            \end{figure}%

@@

           \begin{figure}[hbt]
                \centering
                \includegraphics[scale=.52]{images/final_score_tables.png}
                \caption{TABLES FOR FINAL CRI SCORES}
                \label{fig:final_score_tables}
            \end{figure}

@@

### 2015-03-07 paper_70_case-study.tex
rearranged some figures so they appear more inline with the appropriate content

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/quality_plots1.png}
            \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
            \label{fig:quality-plots1}
        \end{figure}

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/quality_scores.png}
            \caption{CRI QUALITY SCORES}
            \label{fig:quality-scores}
        \end{figure}

@@

        Since percent uptime has already been calculated and no historical
        analysis needs to be performed, the calculation of the scores
        can be performed. 
        R code to compute the CRI availability scores can be found in Appendix
        \ref{src:availability}. Figure \ref{fig:availability-scores} displays
        the CRI availability scores.  As can be seen the scores are all above
        70.  That is good from a performance standpoint, but it might be an
        indication that the expected uptimes could be raised.  If expected
        uptimes are consistently being exceeded, some consideration should
        be given to increase the expected uptimes.  This shows that
        organizations, or at least this particular organization, are getting
        very good at keeping computer systems available.  Therefore,
        SLAs need to be adjusted to properly reflect the better performance.

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.25]{images/schedule_hist.png}
            \caption{SCHEDULE DATA HISTOGRAM WITH CAUCHY}
            \label{fig:schedule-hist}
        \end{figure}

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/schedule_scores.png}
            \caption{CRI SCHEDULE SCORES}
            \label{fig:schedule-scores}
        \end{figure}

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/requirements_scores.png}
            \caption{CRI REQUIREMENTS SCORES}
            \label{fig:requirements-scores}
        \end{figure}

@@

    \subsection{OVERALL}
        Now it is time to combine the scores for the overall CRI.  Notice
        the schedule does not have scores for January 2014 or January 2015.
        Presumably, that is because the SDO within the large financial institution
        does not schedule projects to be completed in January. Much of the work
        would need to be completed over Christmas and New Year's Day, but many
        workers take personal time off of work during that time.  Thus some
        organizations will schedule appropriately.  CRI is well suited to
        handle this problem.  Just perform a weighted average over the
        applicable elements.  In this case study, the weights are all equal,
        so CRI is just a straight average.  Figure \ref{fig:cri-scores}
        displays the CRI scores as computed with the source code
        from Appendix \ref{src:overall}.  The scores are all above 0, so this
        financial institution is consistently performing better
        than expected.

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/cri_scores.png}
            \caption{CRI SCORES}
            \label{fig:cri-scores}
        \end{figure}

    \subsection{CORRELATION AND SENSITIVITY}
        Based upon the graphs for the elements scores, there does not
        appear to be any correlation.  None of the graphs
        rise and fall during the same intervals.  The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.

        To check the sensitivity of the CRI formula, the first method
        from Section \ref{sub:sensitivity} is used.  Small random
        values were added to the input values of the formulas. 
        Then the new values were used to calculated the element scores 
        at the respective Application ID or Project ID level.  Finally
        the new CRI element scores were compared with the previous
        scores from the unaltered data.  The goal is to show small
        changes in the input values result in small changes to the 
        CRI element score.  Figure \ref{fig:sensitivity} shows
        histograms of the new scores compared with the previous scores.
        None of the formulas exhibit too much sensitivity as the 
        histograms all indicate most of the score changes are small,
        as seen by the high peak of the histograms.

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/sensitivity.png}
            \caption{CRI SENSITIVITY ANALYSIS}
            \label{fig:sensitivity}
        \end{figure}

@@

        \begin{longtable}{@{}l rr rrr}
            \toprule%
             \centering%
             {\bfseries CRI Element}
             & {\bfseries Columns Altered } \\

            \cmidrule[0.2pt](r{0.125em}){1-1}%
            \cmidrule[0.2pt](lr{0.125em}){2-2}%
            % \midrule
            \endhead

@@

>>>>

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/quality_plots1.png}
            \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
            \label{fig:quality-plots1}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/quality_scores.png}
            \caption{CRI QUALITY SCORES}
            \label{fig:quality-scores}
        \end{figure}

@@

        Since percent uptime has already been calculated and no historical
        analysis needs to be performed, the calculation of the scores
        can be performed. 
        R code to compute the CRI availability scores can be found in Appendix
        \ref{src:availability}. Figure \ref{fig:availability-scores} displays
        the CRI availability scores.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/availability_scores.png}
            \caption{CRI AVAILABILITY SCORES}
            \label{fig:availability-scores}
        \end{figure}

        As can be seen in Figure  \ref{fig:availability-scores}
        the scores are all above 70 which
        is good from a performance standpoint, but it might be an
        indication that the expected uptimes could be raised.  If expected
        uptimes are consistently being exceeded, some consideration should
        be given to increase the expected uptimes.  This shows that
        organizations, or at least this particular organization, are getting
        very good at keeping computer systems available.  Therefore,
        SLAs need to be adjusted to properly reflect the better performance.

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.25]{images/schedule_hist.png}
            \caption{SCHEDULE DATA HISTOGRAM WITH CAUCHY}
            \label{fig:schedule-hist}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/schedule_scores.png}
            \caption{CRI SCHEDULE SCORES}
            \label{fig:schedule-scores}
        \end{figure}

@@

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/requirements_scores.png}
            \caption{CRI REQUIREMENTS SCORES}
            \label{fig:requirements-scores}
        \end{figure}

@@

    \subsection{OVERALL}
        Now it is time to combine the scores for the overall CRI.
        Schedule does not have scores for January 2014 or January 2015.
        Presumably, that is because the SDO within the large financial institution
        does not schedule projects to be completed in January. Much of the work
        would need to be completed over Christmas and New Year's Day, but many
        workers take personal time off of work during that time.  Thus some
        organizations will schedule appropriately.  CRI is well suited to
        handle this problem.  Just perform a weighted average over the
        applicable elements.  In this case study, the weights are all equal,
        so CRI is just a straight average.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/cri_scores.png}
            \caption{CRI SCORES}
            \label{fig:cri-scores}
        \end{figure}

        Figure \ref{fig:cri-scores}
        displays the CRI scores as computed with the source code
        from Appendix \ref{src:overall}.  The scores are all above 0, so this
        financial institution has performed consistently better
        than expected.

    \subsection{SENSITIVITY AND CORRELATION}

        To check the sensitivity of the CRI formula, the first method
        from Section \ref{sec:sensitivity} is used.  Small random
        values were added to the input values of the formulas. 
        Then the new values were used to calculated the element scores 
        at the respective Application ID or Project ID level.  Finally
        the new CRI element scores were compared with the previous
        scores from the unaltered data.  The goal is to show small
        changes in the input values result in small changes to the 
        CRI element score.  Figure \ref{fig:sensitivity} shows
        histograms of the new scores compared with the previous scores.
        None of the formulas exhibit too much sensitivity as the 
        histograms all indicate most of the score changes are small,
        as seen by the high peak of the histograms.

        \begin{figure}[htb]
            \centering
            \includegraphics[scale=.3]{images/sensitivity.png}
            \caption{CRI SENSITIVITY ANALYSIS}
            \label{fig:sensitivity}
        \end{figure}

@@

        \begin{longtable}{@{}l r}
            \toprule%
             \centering%
             {\bfseries CRI Element}
             & {\bfseries Columns Altered } \\

            \cmidrule[0.2pt](r{0.125em}){1-1}%
            \cmidrule[0.2pt](r{0.125em}){2-2}%
            % \midrule
            \endhead

@@

        The columns were altered by adding
        random noise from a normal distribution with mean 0 and standard
        deviation as explained above.  The only exception to the normal
        distribution was for the schedule element.  The schedule element
        drew its noise from a Cauchy distribution with location and scale
        as defined when determining the distribution of the schedule data.
        That Cauchy distribution can be seen with the histogram in 
        Figure \ref{fig:schedule-hist}.

        Based upon the graphs for the elements scores, there does not
        appear to be any correlation.  None of the graphs
        rise and fall during the same intervals.  The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.
